### 2011-06-21 standing-patches-paper.tex
/* The Next Paper */
updated with notes from train jun 20

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{proportion-by-sigma.eps}
\caption{ %
{\bf Mean proportion of patches arising from standing variation.} The paramters given are for the sickle-cell example.  XXX say more.
}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{proportion-contour.png}
\caption{ %
{\bf Mean proportion of area occupied by standing variants,} as a function of dispersal distance $\sigma$ and selective disadvantage $s_d$.  XXX at what parameters. XXX
}
\end{center}
\end{figure}

@@

@@

Since we don't take this into account... we can ad-hoc it in by using the standing variation calculations -- add this to $\lambda_0$.
This is equivalent to changing $s_d$ by... how much?

Compare to panmixia: increases degree of parallel mutation if... ?

@@

@@

Look at some human parameters?

@@

>>>>

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{proportion-by-sd.eps}
\caption{ %
{\bf Mean proportion of patches arising from standing variation.} The paramters given are for the sickle-cell example.  XXX say more.
}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{charlen-by-sd-sigma.png}
\caption{ %
{\bf Characteristic length,} as a function of dispersal distance $\sigma$ and selective disadvantage $s_d$.  XXX at what parameters. XXX
}
\end{center}
\end{figure}

@@

{\tt Simulations:} compare mean density against $s_d$ at different values of $\sigma$; omit variability if needed for readability.
Compare to panmictic results.

@@

Both these results and the panmictic calculations are underestimates.  
If the time to local fixation is enough to change things significantly, 
we are in the realm where the panmictic results apply better.

Graph: sigma against mean number of origins; different curves for spatial, panmictic (flat), and simulation;
different values of theta as different line types?
Mention Monty's empirical speeds paper.

Compare to panmixia: increases degree of parallel mutation if... ?
Check P and H papers and Orr and Betancourt.  (standing variation only)

@@

{\tt Include cartoon here.}

@@

HbS

lava bed peromyscus

G6PD

@@

discuss mixing of types; 
Graph: from simulation showing local proportions in a single patch showing initial fixation of a single type and later mixing converging toward more than one type.  (and eventual loss of one?)
